Periodic Traveling Waves in an Integro-Difference Equation With a Nonmonotone Growth Function and Strong Allee Effect

### 2021-07-04 paper_draft4.tex
updates

\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{enumerate}
%\usepackage{caption,subcaption}
\usepackage{caption}
\usepackage{subcaption}

@@

\section{Periodic traveling waves}

@@

\begin{enumerate}[(H1)]
\item $k$ is a non-negative Lebesgue-integrable function with $\int_{-\infty}^{\infty} k(x) \, dx = 1$;

@@

\item  for all $\lambda\in(0,1)$, for all $a\in\mathbb R$, the function $x \mapsto k(x)-\lambda k(x-a)$ has at most one zero-crossing in $\mathbb R$.
\end{enumerate}
%\end{hyp}

@@

 Let $w_1$ and $w_2$ be two functions defined by
\begin{equation} \label{w1}
w_1(x) := \int_x^\infty k(y) \, dy
\end{equation}
and
\begin{equation} \label{w2}
w_2(x) := Q[w_1](x) = \int_{-\infty}^{\infty} k(y) g(w_1(x-y)) \, dy 
\end{equation}

Hypothesis (H1) implies $w_1$ and $w_2$ have well-defined limits at $\pm\infty$ given by $w_1(\infty)=w_2(\infty)=0$, $w_1(-\infty)=1$, and $w_2(-\infty)=\m$. Furthermore, $w_1$ is monotonically decreasing, while $w_2$ may be non-monotonic.

\begin{lem} \label{lemma1}
If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then there exists unique $c^*\in\mathbb R$ such that $Q[w_2](x)=w_1(x-2c^*)$ for all $x\in\mathbb R$.
\end{lem}

\begin{proof} Let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$. Since $w_1$ is monotone, it follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$. Applying the integro-difference operator to $w_1$ yields
\begin{equation} \label{qw1calculation}
\begin{aligned}
Q[w_1](x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy
\end{aligned} \end{equation}

Taking the derivative with respect to $x$, we find
\begin{equation}\label{dw2dx}
\frac{dw_2}{dx} = -k(x-x_\a) + (1-\m)k(x-x_\b)
\end{equation}

From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point. This leaves two cases:
\begin{enumerate}[{Case} 1.]
\item If $w_2$ has no turning points, it must be monotonically decreasing.
\item If $w_2$ has a single turning point $x^*$, then $w_2(x)$ is increasing on $(-\infty,x^*)$ and decreasing on $(x^*,\infty)$, with $\m \leq w_2(x^*)\leq \b$.
\end{enumerate}

In both cases, $w_2(x)$ has a well-defined right inverse on the open interval $(0,\m)$. Since $0<\a<\m$, let
\begin{equation}
c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid w_2(x)\geq\a\}
\end{equation}

It follows that $w_2(x)\geq\a$ for $x\leq 2c^*$ and $w_2(x)<\alpha$ for $x>2c^*$. Along with the assumption that $\sup_{x\in\mathbb R}w_2(x)\leq\b$, we can apply the integro-difference operator once more:
\begin{equation} \begin{aligned}
Q[w_2](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_2(y)) \, dy \\
&= \int_{-\infty}^{2c^*} k(x-y) \, dy \\
&= \int_{x-2c^*}^{\infty} k(y) \, dy &= w_1(x-2c^*).
\end{aligned} \end{equation}
%By defining $c^* = \frac{1}{2}x_0$, and applying the integro-difference operator, we can see that $w_1$ and $w_2$ are both solutions to the periodic traveling wave equation with mean speed $c^*$:
%\begin{equation}
%Q^2[w_1](x) = w_1(x-2c^*); \quad Q^2[w_2](x) = w_2(x-2c^*)
%\end{equation}
\end{proof}

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{figures/fig2A.png}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{figures/fig2B.png}
  \label{fig:sub2}
\end{subfigure}
\caption{Plots of $w_1(x)$ (left) and $w_2(x)$ (right) with the Laplace dispersal kernel and growth parameters $\alpha=0.3$, $\mu=0.5$, and $\beta=0.8$}
\label{fig:test}
\end{figure}

@@

\begin{thm} \label{theorem1}
If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then the recurrence \eqref{q} has a periodic traveling wave solution $(u_n)_{n=0}^{\infty}$ satisfying
%\begin{equation} \label{ptw}
%u_n(x) = \begin{cases}
%w_1(x-nc^*) & n \text{ even} \\
%w_2(x-nc^*) & n \text{ odd}
%\end{cases}
%\end{equation}

\begin{equation} \label{ptw}
\begin{aligned}
u_{2n}(x) &= w_1(x-2nc^*) \\
u_{2n+1}(x) &= w_2(x-2nc^*)
\end{aligned}
\end{equation}
for all $n \geq 0$.
\end{thm}

\begin{proof}
It suffices to show that equation \eqref{ptw} satisfies $u_{n+1}=Q[u_n]$ for all $n \geq 0$. For convenience, we will switch the index and consider the cases $u_{2n}$ and $u_{2n+1}$ separately. The basic case, $u_1 = Q[u_0]$, follows immediately from definition \ref{w2}. This proves the first half. Next, we have $u_2(x)=w_1(x-2c^*)$, which follows by Lemma \ref{lemma1}.

For the inductive step, suppose $u_{2n+1}=Q[u_{2n}]$ and $u_{2n+2}=Q[u_{2n+1}]$ for some $n\geq 0$. We only need to show $u_{2n+3}=Q[u_{2n+2}]$. We have
\begin{equation} \begin{aligned}
u_{2n+3}(x) &= w_2(x-2nc^*-2c^*) \\
&= Q^2[w_2](x-2nc^*) \\
&= Q^2[u_{2n+1}](x) \\ 
&= Q[u_{2n+2}](x)
\end{aligned} \end{equation}
\end{proof}

\begin{figure}[h!] 
\centering
  \caption{Numerical simulation of the integro-difference equation with Laplace dispersal kernel, $\alpha=0.2$, $\mu=0.3$, and $\beta=0.8$. Later timepoints are colored in red, with earlier timepoints colored in green.}
\label{fig3}
  \includegraphics{figures/fig3.png}
\end{figure}

@@

\begin{equation} \begin{aligned}
\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)
&= \lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}w_2(x-2nc^*) \\
&= \lim_{n\to\infty}\inf_{x<-2n\epsilon}w_2(x) \\
&= \liminf_{x\to-\infty}w_2(x) \\ &= m.
\end{aligned} \end{equation}

@@

@@

\begin{thm} Suppose $k(x)$ has compact support and $\sup_{x\in\mathbb R}w_2(x)\leq \b$. Let $u_0(x)$ be a non-negative continuous function, and let $A=\{x\in\mathbb R:\a\leq u_0(x)\leq \b\}$. If $A$ is connected with sufficiently large radius and $c^* \geq 0$, then the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.
\begin{equation}
\lim_{n\to\infty}\inf_{|x|<n(c^*-\epsilon)}u_{n}(x)>0,
\end{equation}
and 
\begin{equation}
\lim_{n\to\infty}\sup_{|x|>n(c^*+\epsilon)}u_n(x)=0.
\end{equation}
for all $\epsilon>0$.
\end{thm}

\begin{proof}
By the translation invariance property of $Q$, we may assume without loss of generality $A=[-r,r]$, for some $r>0$. It follows that $u_0(x)<\a$ for $|x|>r$ and $\a\leq u_0(x)\leq\b$ for $|x| \leq r$. Furthermore, there exists $\sigma>0$ such that $k(x)>0$ if and only if $|x|<\sigma$.

Assuming $r \geq \frac{\sigma}{2}$, we have
\begin{equation} \begin{aligned}
u_1(x) = Q[u_0](x) &= \int_{-r}^{r} k(x-y) \, dy \\
&= \begin{cases}
w_1(x-r) & x \geq 0 \\
w_1(-x+r) & x< 0
\end{cases}
\end{aligned}  \end{equation}

Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. Then, applying the growth function, we have
\begin{equation} g(u_1(x)) = \begin{cases}
0 & x<-r-x_\a \\
1 & -r-x_\a \leq x \leq -r-x_\b \\
m & -r-x_\b < x < r+x_\b \\
1 & r+x_\b \leq x \leq r+x_\a \\
0 & x > r+x_\a
\end{cases}
\end{equation}
Note that $g(u_1(x))=g(w_1(x))$ for all $x >-r-x_\b$. Thus $Q[u_1](x)=(k*(g\circ u_1))(x)=(k*(g\circ w_1))(x)=Q[w_1](x)$ for all $x>-r-x_\b+\sigma$. If we assume $r \geq x_\b+\sigma$, then $u_2(x)=Q[u_1](x)=Q[w_1](x-r)=w_2(x-r)$ for $x>0$.

By symmetry of the integro-difference operator, $Q[u_1](x) = Q[w_1](-x+r)$ for $x<0$. Thus,

\begin{equation}
u_2(x) = Q[u_1](x) = \begin{cases}
w_2(x-r) & x \geq 0 \\
w_2(-x+r) & x < 0 
\end{cases}
\end{equation}
Since $c^*\geq 0$, we have
\begin{equation}
g(u_2(x)) = \begin{cases}
0 & x < -r-2c^* \\
1 & -r-2c^* \leq x \leq r+2c^* \\
0 & x > r+2c^* 
\end{cases}
\end{equation}

Thus,
\begin{equation}
u_3(x) = Q[u_2](x) = \begin{cases}
w_1(x-r-2c^*) & x \geq 0 \\
w_1(-x+r+2c^*) & x < 0 
\end{cases}
\end{equation}

The preceding argument can be repeated inductively to obtain
\begin{equation}
u_{2n+1}(x) = w_1(|x|-r-2nc^*)
\end{equation}
and
\begin{equation}
u_{2n+2}(x) = w_2(|x|-r-2nc^*)
\end{equation}
for all $n\geq 0$.
\end{proof}

@@

>>>>

\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
%\usepackage{geometry}
\usepackage{graphicx}
\usepackage{enumerate}
%\usepackage{caption,subcaption}
\usepackage{caption}
\usepackage{subcaption}

@@

\section{Results}

\subsection{Periodic traveling waves}

@@

\begin{enumerate}[(H1)]
\item $k$ is a non-negative, Lebesgue-integrable function with $\int_{-\infty}^{\infty} k(x) \, dx = 1$;

@@

\item  for all $\lambda\in(0,1)$, for all $a\in\mathbb R$, the function $x \mapsto k(x)-\lambda k(x-a)$ has at most one zero-crossing in $\mathbb R$.
\end{enumerate}

Hypothesis (H1) indicates that the dispersal kernel accounts for all individuals, while hypothesis (H2) guarantees the disperal process is symmetric.

%\end{hyp}

@@

 Let $w_1$ and $w_2$ be two functions defined by
\begin{equation} \label{w1}
w_1(x) := \int_x^\infty k(y) \, dy
\end{equation}
and
\begin{equation} \label{w2}
w_2(x) := Q[w_1](x+c^*) = \int_{-\infty}^{\infty} k(y) g(w_1(x+c^*-y)) \, dy 
\end{equation} 
with $c^* \in \mathbb R$ a constant given by
\begin{equation}
c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid Q[w_1](x)\geq\a\}
\end{equation}

Note that $c^*$ is finite by the intermediate value theorem since $Q[w_1](\infty)=0$ and $Q[w_1](-\infty)=\m$ with $0<\a<\m$.

\begin{lem} \label{lemma0}
$w_1(x)$ is monotone, while $w_2(x)$ has at most one turning point.
\end{lem}

\begin{proof}
The monotonicity of $w_1$ follows since $w_1'(x)=-k(x)\leq 0$ by hypothesis (H1). To count the turning points of $w_2$, let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$. Since $w_1$ is monotone, it follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$. Applying the integro-difference operator to $w_1$ yields
\begin{equation} \label{qw1calculation}
\begin{aligned}
Q[w_1](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy
\end{aligned} \end{equation}

Taking the derivative with respect to $x$, we find
\begin{equation}\label{dw2dx}
\frac{d}{dx}Q[w_1] = -k(x-x_\a) + (1-\m)k(x-x_\b)
\end{equation}

From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point.
\end{proof}

%
%Hypothesis (H1) implies $w_1$ and $w_2$ have well-defined limits at $\pm\infty$ given by $w_1(\infty)=w_2(\infty)=0$, $w_1(-\infty)=1$, and $w_2(-\infty)=\m$. Furthermore, $w_1$ is monotonically decreasing, while $w_2$ may be non-monotonic.

%\begin{lem} \label{lemma1}
%If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then $Q[w_2](x)=w_1(x-c^*)$ for all $x\in\mathbb R$.
%\end{lem}

\begin{lem} \label{lemma1}
If $ ||w_2||_\infty \leq \b$, then $Q[w_2](x)=w_1(x-c^*)$ for all $x\in\mathbb R$.
\end{lem}

\begin{proof}
By Lemma \ref{lemma0}, $w_2(x)$ has either zero or one turning point(s). In the first case, $w_2(x)$ is monotonically decreasing and satisfies $w_2(x) \geq \a$ for $x \leq c^*$ and $w_2(x) < \a$ for $x > c^*$. In the second case, $w_2(x)$ has a unique turning point $x_0 \in \mathbb R$; it follows that $w_2(x)$ is monotonically increasing on $(-\infty,x_0)$ and monotonically decreasing on $(x_0,\infty)$, and $x_0$ is a global maximum. By the assumption $w_2(x)\leq\beta$ for all $x$, we have $w_2(x_0)\leq\beta$. It follows that $c^* \in (x_0,\infty)$, and $w_2(x)$ satisfies $g(w_2(x))=1$ for $x<c^*$ and $g(w_2(x)) = 0$ for $x>c^*$. In both cases, we have

%Let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$. Since $w_1$ is monotone, it follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$. Applying the integro-difference operator to $w_1$ yields
%\begin{equation} \label{qw1calculation}
%\begin{aligned}
%Q[w_1](x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
%&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
%&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy
%\end{aligned} \end{equation}
%
%Taking the derivative with respect to $x$, we find
%\begin{equation}\label{dw2dx}
%\frac{d}{dx}Q[w_1] = -k(x-x_\a) + (1-\m)k(x-x_\b)
%\end{equation}

%From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point. This leaves two cases:
%\begin{enumerate}[{Case} 1.]
%\item If $w_2$ has no turning points, it must be monotonically decreasing.
%\item If $w_2$ has a single turning point $x^*$, then $w_2(x)$ is increasing on $(-\infty,x^*)$ and decreasing on $(x^*,\infty)$, with $\m \leq w_2(x^*)\leq \b$.
%\end{enumerate}
%
%In both cases, $w_2(x)$ has a well-defined right inverse on the open interval $(0,\m)$. Since $0<\a<\m$, let
%\begin{equation}
%c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid w_2(x)\geq\a\}
%\end{equation}

%It follows that $w_2(x)\geq\a$ for $x\leq 2c^*$ and $w_2(x)<\alpha$ for $x>2c^*$. Along with the assumption that $\sup_{x\in\mathbb R}w_2(x)\leq\b$, we can apply the integro-difference operator once more:
\begin{equation} \begin{aligned}
Q[w_2](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_2(y)) \, dy \\
&= \int_{-\infty}^{c^*} k(x-y) \, dy \\
&= \int_{x-c^*}^{\infty} k(y) \, dy \\
&= w_1(x-c^*).
\end{aligned} \end{equation}
%By defining $c^* = \frac{1}{2}x_0$, and applying the integro-difference operator, we can see that $w_1$ and $w_2$ are both solutions to the periodic traveling wave equation with mean speed $c^*$:
%\begin{equation}
%Q^2[w_1](x) = w_1(x-2c^*); \quad Q^2[w_2](x) = w_2(x-2c^*)
%\end{equation}
\end{proof}

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/fig2A.png}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/fig2B.png}
  \label{fig:sub2}
\end{subfigure}
\caption{Plots of $w_1(x)$ (left) and $w_2(x)$ (right) with the Laplace dispersal kernel $k(x)=\frac{1}{2}e^{-|x|}$ and growth parameters $\alpha=0.3$, $\mu=0.5$, and $\beta=0.8$.}
\label{fig:test}
\end{figure}

@@

\begin{thm} \label{theorem1}
If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then equation \eqref{q} has a periodic traveling wave solution given by %$(u_n)_{n=0}^{\infty}$ satisfying
%\begin{equation} \label{ptw}
%u_n(x) = \begin{cases}
%w_1(x-nc^*) & n \text{ even} \\
%w_2(x-nc^*) & n \text{ odd}
%\end{cases}
%\end{equation}

\begin{equation} \label{ptw}
u_n(x) = \begin{cases}
w_1(x-nc^*) & n \text{ even} \\
w_2(x-nc^*) & n \text{ odd}
\end{cases}
\end{equation}
for all $n \geq 0$.
\end{thm}

\begin{proof}
It suffices to show that equation \eqref{ptw} satisfies $u_{n+1}=Q[u_n]$ for all $n \geq 0$. If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*-c^*)$. Applying the integro-difference operator, we obtain
\begin{equation} \begin{aligned}
Q[u_n](x) &= Q[w_1](x-nc^*) \\
&= w_2(x-nc^*-c^*) \\
&= u_{n+1}(x)
\end{aligned} \end{equation}
by \eqref{w2}. On the other hand, if $n$ is odd, then $n+1$ is even, so $u_n(x)=w_2(x-nc^*)$ and $u_{n+1}(x)=w_1(x-nc^*-c^*)$. Applying the operator, we get
\begin{equation} \begin{aligned}
Q[u_n](x) &= Q[w_2](x-nc^*) \\
&= Q^2[w_1](x-nc^*+c^*) \\
&= w_1(x-nc^*-c^*) \\
&= u_{n+1}(x)
\end{aligned} \end{equation}
by Lemma \ref{lemma1}.
\end{proof}

%For convenience, we will switch the index and consider the cases $u_{2n}$ and $u_{2n+1}$ separately. The basic case, $u_1 = Q[u_0]$, follows immediately from definition \ref{w2}. This proves the first half. Next, we have $u_2(x)=w_1(x-2c^*)$, which follows by Lemma \ref{lemma1}.
%
%For the inductive step, suppose $u_{2n+1}=Q[u_{2n}]$ and $u_{2n+2}=Q[u_{2n+1}]$ for some $n\geq 0$. We only need to show $u_{2n+3}=Q[u_{2n+2}]$. We have
%\begin{equation} \begin{aligned}
%u_{2n+3}(x) &= w_2(x-2nc^*-2c^*) \\
%&= Q^2[w_2](x-2nc^*) \\
%&= Q^2[u_{2n+1}](x) \\ 
%&= Q[u_{2n+2}](x)
%\end{aligned} \end{equation}
% \end{proof}

\begin{figure}[h!] 
\centering
  \caption{Numerical simulation of the integro-difference equation with Laplace dispersal kernel, $\alpha=0.2$, $\mu=0.3$, and $\beta=0.8$. Later timepoints are colored in red, with earlier timepoints colored in green.}
\label{fig3}
  \includegraphics[width=.8\linewidth]{figures/fig3.png}
\end{figure}

@@

\begin{equation} \begin{aligned}
\lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}u_{2n+1}(x)
&= \lim_{n\to\infty}\inf_{x<2n(c^*-\epsilon)}w_2(x-2nc^*) \\
&= \lim_{n\to\infty}\inf_{x<-2n\epsilon}w_2(x) \\
&= \liminf_{x\to-\infty}w_2(x) \\ &= \m.
\end{aligned} \end{equation}

@@

\subsection{Compactly supported kernels}

@@

\begin{lem}
Suppose $k(x)$ has support $[-\sigma,\sigma]$ and $c^*\geq0$.

\begin{enumerate}
\item If $r \geq \sigma - x_\b$, then $Q[w_1](|x|-r) = w_2(|x|-r-c^*)$.

\item 
\end{enumerate}
\end{lem}

\begin{proof}
\begin{enumerate}
\item 
Let $u(x) = w_1(|x|-r)$. Assuming $r+x_\b \geq 0$, i.e. $r \geq -x_\b$, we have $g(u(x)) = \m$ for $|x| < r+x_\b$, $g(u(x)) = 1$ for $r+x_\b \leq x \leq r+x_\a$, and $g(u(x)) = 0 $ for $x > r+x_\a$. Note that $g(u(x)) = g(w_1(x-r))$ for $x \geq -r-x_\b$. Applying the convolution operator, $Q[u](x) = Q[w_1](x-r)$ for $x \geq -r-x_\b+\sigma$. Assuming $r \geq \sigma - x_\b$, this shows $Q[u](x) = w_2(x-r-c^*)$ for $x \geq 0$. By the symmetry of $k(x)$, we have $Q[u](x) = w_2(|x|-r-c^*)$.

\item 
Let $u(x) = w_2(|x|-r)$. Assuming $r+x_\b \geq 0$, i.e. $r \geq -x_\b$, we have $g(u(x)) = \m$ for $|x| < r+x_\b$, $g(u(x)) = 1$ for $r+x_\b \leq x \leq r+x_\a$, and $g(u(x)) = 0 $ for $x > r+x_\a$. Note that $g(u(x)) = g(w_1(x-r))$ for $x \geq -r-x_\b$. Applying the convolution operator, $Q[u](x) = Q[w_1](x-r)$ for $x \geq -r-x_\b+\sigma$. Assuming $r \geq \sigma - x_\b$, this shows $Q[u](x) = w_2(x-r-c^*)$ for $x \geq 0$. By the symmetry of $k(x)$, we have $Q[u](x) = w_2(|x|-r-c^*)$.
\end{enumerate}
\end{proof}

\begin{thm} Suppose $k(x)$ has compact support and $\sup_{x\in\mathbb R}w_2(x)\leq \b$. Let $u_0(x)$ be non-negative and continuous function, and suppose $\a \leq u_0(x) \leq \b$ for $|x| \leq r$ and $u_0(x) < \a$ otherwise, for some $r > 0$. If $r$ is sufficiently large and $c^* \geq 0$, then the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.
\begin{equation}
\lim_{n\to\infty}\inf_{|x|<n(c^*-\epsilon)}u_{n}(x)>0,
\end{equation}
and 
\begin{equation}
\lim_{n\to\infty}\sup_{|x|>n(c^*+\epsilon)}u_n(x)=0.
\end{equation}
for all $\epsilon>0$.
\end{thm}

\begin{thm} Suppose $k(x)$ has compact support and $||w_2||_\infty \leq \b$. If $c^* \geq 0$ and $r$ is sufficiently large, then equation \eqref{q} has a periodic spreading solution given by
\begin{equation} \label{compactptw}
u_n(x) = \begin{cases}
w_1(|x|-r-nc^*) & n \text{ even} \\
w_2(|x|-r-nc^*) & n \text{ odd}
\end{cases}
\end{equation}
for all $n\geq 0$.
\end{thm}

\begin{proof}
As in the proof of Theorem \ref{theorem1}, it suffices to show $u_{n+1}=Q[u_n]$ for all $n\geq 0$. If $n$ is even, we have $u_n(x)=w_1(|x|-r-nc^*)$. Assuming $r \geq \sigma$ and $c^* \geq 0$, this implies $g(u_n(x)) = 0$ for $|x| > r+nc^*+x_\a$, $g(u_n(x))=1$ for $r+nc^*+x_\b\leq |x|\leq r+nc^*+x_\a$, and $g(u_n(x))=\m$ for $|x|<r+nc^*+x_\b$. Note that $g(u_n(x)) = g(w_1(x-r-nc^*))$ for $x \geq -r-nc^*-x_\b$. Applying the convolution operator, we have $Q[u_n](x) = Q[w_1](x-r-nc^*)$ for $x \geq -r-nc^*-x_\b+\sigma$. Assuming $r \geq \sigma - x_\b$, it follows that $Q[u_n](x) = Q[w_1](x-r-nc^*)$ for $x \geq 0$. By hypothesis (H2), $k(x)$ is an even function, thus $Q[u_n](-x) = Q[u_n](x)$, hence $Q[u_n](x) = Q[w_1](|x|-r-nc^*)$ for all $x \in \mathbb R$, i.e. $u_{n+1}(x) = w_2(|x|-r-nc^*-c^*)$. Note that the preceding calculation requires $r \geq \max\{\sigma,\sigma-x_\b\}$; a sufficient condition is $r \geq 2\sigma$.

If $n$ is odd, then $u_n(x)=w_2(|x|-r-nc^*)$, and for $r\geq0$ and $c^*\geq 0$ it follows that $g(u_n(x)) = 0$ for $|x| > r+nc^*+c^*$ and $g(u_n(x))=1$ for $|x| \leq r+nc^*+c^*$.

UNFIN
\end{proof}

%
%We apply induction on $n$. For the basis case, it is sufficient to show $u_1(x) = w_1(|x|-r)$ for all $x$. It follows from the definition of $u_0(x)$ that $g(u_0(x))=1$ for $|x|\leq r$ and $g(u_0(x))=0$ otherwise. Assuming $r \geq \frac{\sigma}{2}$, we have $u_1(x)=Q[u_0](x)=w_1(x-r)$ for $x\geq 0$. By hypothesis (H2), $k(x)$ is an even function, so $u_1(x)=u_1(-x)$, i.e. $u_1(x)=w_1(-x+r)=w_1(x-r)$ for $x<0$. This proves $u_1(x)=w_1(|x|-r)$ for all $x$.
%
%For the inductive step, suppose equation \eqref{compactptw} holds for some $n\geq0$. If $n$ is even, the inductive hypothesis yields $u_{n+1}(x)=w_1(|x|-r-nc^*)$.
%\end{proof}
%
%\begin{proof}
%By the translation invariance property of $Q$, we may assume without loss of generality $A=[-r,r]$, for some $r>0$. It follows that $u_0(x)<\a$ for $|x|>r$ and $\a\leq u_0(x)\leq\b$ for $|x| \leq r$. Furthermore, there exists $\sigma>0$ such that $k(x)>0$ if and only if $|x|<\sigma$. Assuming $r \geq \frac{\sigma}{2}$, we have
%\begin{equation} \begin{aligned}
%u_1(x) = Q[u_0](x) &= \int_{-r}^{r} k(x-y) \, dy \\
%&= \begin{cases}
%w_1(x-r) & x \geq 0 \\
%w_1(-x+r) & x< 0
%\end{cases}
%\end{aligned}  \end{equation}
%
%Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. Then, applying the growth function, we have
%\begin{equation} g(u_1(x)) = \begin{cases}
%0 & x<-r-x_\a \\
%1 & -r-x_\a \leq x \leq -r-x_\b \\
%m & -r-x_\b < x < r+x_\b \\
%1 & r+x_\b \leq x \leq r+x_\a \\
%0 & x > r+x_\a
%\end{cases}
%\end{equation}
%Note that $g(u_1(x))=g(w_1(x))$ for all $x >-r-x_\b$. Thus $Q[u_1](x)=(k*(g\circ u_1))(x)=(k*(g\circ w_1))(x)=Q[w_1](x)$ for all $x>-r-x_\b+\sigma$. If we assume $r \geq x_\b+\sigma$, then $u_2(x)=Q[u_1](x)=Q[w_1](x-r)=w_2(x-r)$ for $x>0$.  By symmetry of the integro-difference operator, $Q[u_1](x) = Q[w_1](-x+r)$ for $x<0$. Thus,
%
%\begin{equation}
%u_2(x) = Q[u_1](x) = \begin{cases}
%w_2(x-r) & x \geq 0 \\
%w_2(-x+r) & x < 0 
%\end{cases}
%\end{equation}
%Since $c^*\geq 0$, we have
%\begin{equation}
%g(u_2(x)) = \begin{cases}
%0 & x < -r-2c^* \\
%1 & -r-2c^* \leq x \leq r+2c^* \\
%0 & x > r+2c^* 
%\end{cases}
%\end{equation}
%
%Thus,
%\begin{equation}
%u_3(x) = Q[u_2](x) = \begin{cases}
%w_1(x-r-2c^*) & x \geq 0 \\
%w_1(-x+r+2c^*) & x < 0 
%\end{cases}
%\end{equation}
%
%The preceding argument can be repeated inductively to obtain
%\begin{equation}
%u_{2n+1}(x) = w_1(|x|-r-2nc^*)
%\end{equation}
%and
%\begin{equation}
%u_{2n+2}(x) = w_2(|x|-r-2nc^*)
%\end{equation}
%for all $n\geq 0$.
%\end{proof}

@@

\subsection{Variability in wave speed}
